---
title: "WineQuality.Rmd"
author: "inteRstellar"
date: "13/5/2022"
output:
  word_document: default
  pdf_document: default
---
## Point 1
Wine Dataset 

```{r, include=FALSE}
#knitr.duplicate.label = "allow"
#options(knitr.duplicate.label = "allow")
#knitr.duplicate.label = "allow"

#Libraries-------------------
library(ISLR)
library(tidyverse)
library(glmnet) 
library(grpreg) 
library(mvtnorm)
library(ggplot2)
require(class)
require(pROC)
require(GGally)
require(factoextra)
library(plotly)
library(MASS)
require(gam)
library(cluster)
library(ggpubr)
library(mclust)
require(gridExtra)
require(grid)
require(splines)
require(mgcv)
require(rmarkdown)
library(magrittr)
require(dplyr)
```
## Point 2
### Data load 
```{r, include=FALSE}
#data load
data <- read_delim("WineQuality.csv", delim=",")
glimpse(data) #first let's look at the data
summary(data)
dim(data) #size of the dataset
```
### Cleaning the dataset:
-NAs
-duplicate
-outliers
```{r,results='hide',fig.keep='all'}
#all the variables are numeric 
#omitting the NAs
data <- na.omit(data)
#deleting the duplicates
any(duplicated(data)) #we see that there are some duplicates
data <-distinct(data)  #so we get rid of it
#Removing outliers
dim(data) #dim of rows and cols
boxplot(data, col="darkgreen")
data <- data.frame(data)
#remove the outliers from every predictor except quality
for(i in colnames(data)[1:11]) { 
  print(colnames(data))
  quartiles <- quantile(data[,i], probs=c(.15, .95), na.rm = FALSE)
  IQR <- IQR(data[,i])
  Lower <- quartiles[1] - 1.5*IQR
  Upper <- quartiles[2] + 1.5*IQR 
  data<- subset(data, data[,i] > Lower & data[,i] < Upper)
}
```
Then we check that outliers has been removed
```{r,results='hide',include=FALSE}
boxplot(data, font.main=3, cex.main=1.2, xlab="quality",col="darkgreen")
```

### Insights on data 
```{r}
#variable quality seems to be discrete
plot(data$quality, ylab="quality", col="lightgreen")
table(data$quality)
table(data$quality)/length(data$quality)
```

#### We want to look at the most significant variables: 
we want to look at the most significant variables: we choose the correlation matrix

#### Correlation between data
We observe that there is very high correlation in absolute values between alcohol and quality, residual sugar and density, alcohol and density
``` {r}
data %>% cor() %>% corrplot::corrplot() 
```
```{r}
data %>%  ggcorr()
```

#### We then plot the relations between alcohol, residual.data and density

``` {r}
p1 = ggplot(data, aes(x=alcohol, y=density))+ geom_point(alpha=0.5,col="lightsalmon")
p2 =ggplot(data, aes(x=residual.sugar, y=density))+geom_point(alpha=0.5,col="forestgreen")
grid.arrange(p1,p2)
```

#### Barplot to show the distribution of quality in wines:

most wines have quality 5,6 or 7

``` {r}
data2 <-data.frame(data)
quality_count <- data2 %>%
  group_by(quality) %>%
  summarise(counts = n())
ggplot(quality_count, aes(x = quality, y = counts)) +
  geom_bar(fill = "#0073C2FF", stat = "identity") +
  geom_text(aes(label = counts), vjust = -0.3) + 
  theme_pubclean()
```

We confirm that there is a positive linear relationship between alcohol and quality: for high values of quality (6,7,8) there are high values of alcohol

```{r, include=FALSE}
require(radarchart)
require(fmsb)
```

#### Values of alcohol by quality labels

```{r,results='hide',fig.keep='all'}
options(repr.plot.width=7, repr.plot.height=5.5)  #Setting the plot size
alcohol.quality <- data %>%
  group_by(quality) %>%
  summarise(alcohol_mean = mean(alcohol))
alcohol_quality <- as.data.frame(t(alcohol.quality))
names(alcohol_quality) <- paste('Quality',alcohol_quality[1,], sep = '-')
alcohol_quality <- alcohol_quality[2,]
alcohol_quality=rbind(rep(12.4,6) , rep(9.6,6) , alcohol_quality)
radarchart(alcohol_quality, axistype=1, calcex = 0.8, vlcex=0.9,
           caxislabels = c('8,40','','10.50','','14.20'))
```

#### Alcohol in wines

```{r}
curve1 <- ggplot(data, aes(x = alcohol,)) +
  geom_density(color="#FF66FF", fill="salmon") + labs(title="alcohol in the wines")
curve1+geom_vline(aes(xintercept=mean(alcohol)),
                  color="blue", linetype="twodash", size=0.25)
```
Most wines have a density value between 0,90 and 1 
```{r}
data2 %>%
  ggplot(aes(x = density, fill = cut(quality, 100))) + 
  geom_histogram(show.legend = FALSE, bins=50) 
```

#### Insights on volatile acidity against density:
there seems to be a normal distribution 
```{r}
curve1<-ggplot(data, aes(x = volatile.acidity)) +geom_density(color="#FF66FF", fill="lightblue") + labs(title="Volatile acidity  density")
curve1+geom_vline(aes(xintercept=mean(volatile.acidity)),color="blue", linetype="twodash", size=0.25)
```

#### Barplot of correlation between every feature and the wine quality
We can observe that the variables with highest correlation with quality in absolute value are alcohol, density and chlorides
``` {r, echo=FALSE,results='hide',fig.keep='all'}
data.cor <- as.matrix(cor(data))
data.cor
Wine_Feature<-c(colnames(data))
Wine_Feature<-Wine_Feature[-12]
Correlation_with_WineQuality<-c(data.cor[12,])
Correlation_with_WineQuality<-Correlation_with_WineQuality[-12]
df.corr<-data.frame(Wine_Feature,Correlation_with_WineQuality)
library(data.table)
df.corr<-setDT(df.corr)[order(-abs(Correlation_with_WineQuality)), .SD, by = Wine_Feature]
df.corr
df.corr$Wine_Feature <- factor(df.corr$Wine_Feature, levels = df.corr$Wine_Feature)
ggplot(df.corr,aes(x=Wine_Feature,y=Correlation_with_WineQuality))+geom_bar(stat='identity',fill='lightblue', color="darkblue")
```
Then we scale the dataeset
```{r,results='hide'}
data %<>% scale()
```

## Point 3
This dataset contains information about the white variant of the Portuguese Vinho Verde. Wine samples are recorded on the rows.
There exist lots of different markets for wines, each differs in quality and consequently in prices. In a business perspective it is undoubtedly important to catch the correct quality of the in working wine and consequently to sell it at the right price.
In order to do it we built a regression algorithm that predicts the quality of the wine based on some chemicals predictors. 
To compare the models we used the MSE since it is very penalizing in case the difference between the right quality and the predicted wine's quality differs a lot. 

## Point 4
We moreover investigate regarding which of the variables are meaningful by implementing different models and interpreting them.

#### Try to fit a simple linear model to see at first sight which predictors may be significant

``` {r}
linear_model <- lm(quality~., data = data2)
confint(linear_model, level = 0.95)
```
``` {r, echo=FALSE,results='hide'}
summary(linear_model)
summary(linear_model)$r.squared
summary(linear_model)$adj.r.squared
```
from the very beginning we may observe that these predictors are not significant ant that
total sulfur dioxide,chlorides ,citric acid, this has low significance :fixed acidity
we can see that these predictors instead have very low p-values and so high significance
volatile acidity, residual sugar, density and alcohol
we can conclude with 95% confidence that there is no evidence of a relationship between citric acid or total.sulfur.dioxide and the wine quality because 0 is included in their confint.

#### Consequently we try to fit some models only with the expected significant predictors
#### Multiple linear regression
``` {r}
poly <- lm(quality~alcohol + volatile.acidity, data = data2) 
confint(poly, level = 0.95)
summary(poly)
```
The model is: E[quality] = beta0 + beta1alcohol + beta2volatile.acidity= 
2,64 + alcohol * 0,34 – volatile.acidity* 1,57 in this case both predictors are significant
We observe that if the alcohol increase of 1 unit the expected quality to increases by around 0,34 , but an increase in volatile.acidity will decrease the expected quality by 1,57 We can be 95% confident that the true value of alcohol is between 0,32 and 0,36 while for volatile.acidity it is between -1,85 and -1,29

#### Adding an interaction term

``` {r}
inter <- lm(quality~ alcohol+ volatile.acidity + volatile.acidity*alcohol, data=data2) #alternative and more compact way
confint(inter, level = 0.95)
summary(inter)
```

The model is: E[quality] = beta0 + beta1*alcohol + beta2*volatile.acidity + beta3*alcoholvolatile.acidity = 
5,22 + 0.1*alcohol -10.31*volatile.acidity +0.82*alcohol*volatile.acidity
Notice that the term B2 is estimated to be negative, so, for example:
An increase of alcohol increases the response of 0.1 + 0.82*volatile.acidity, but when volatile.acidity increases of one unit the response decreases by 10.31 but increases by 0.82* alcohol

#### Using Gam to individuate the best most meaningful variables
```{r}
ooGam <- gam::gam(quality~., data = data2, control = gam.control(maxit=100))
summary(ooGam)
```
We can observe that for this model all the predictors are meaningful, except for citric.acid

## Point 5

### Splitting of the dataset

```{r,results='hide'}
set.seed(123)
idx <- sample(nrow(data), 0.75*nrow(data))
d_train <- data[idx, ]
d_test <- data[-idx,]
d_ft <-data.frame(d_train)
d_ftest <-data.frame(d_test)
test_quality <- d_ftest$quality
summary(d_ftest)
d_ftest1 <- d_ftest
d_ftest = d_ftest %>% dplyr::select(-quality)
```

### Subset selection 

``` {r}
library (leaps)
regfit.full <- regsubsets(quality~., d_ft, nvmax= 11)
summary(regfit.full)
```
Best 2 variable model contains only volatile.acidity and alcohol.

```{r, echo=FALSE,results='hide'}
reg.summary <- summary(regfit.full)
reg.summary$bic
```

bic decreases as the number of variables inside the model increase until more than 7 variables are inserted.

```{r}
par(mfrow = c(2, 2))
plot(reg.summary$bic , xlab = "Number of Variables",
     ylab = " BIC ", type = "l")
which.min(reg.summary$bic)
points(7, reg.summary$bic[7], col = " red ", cex = 2,pch = 20)
coef(regfit.full , 7)
```

The model with lowest bic is with 7 variables coefficient for the model with lowest bic
fitting the model with the 7 best predictors resulting from the bic

```{r, echo=FALSE,results='hide'}
bic_best <- lm(quality~fixed.acidity+volatile.acidity+residual.sugar+free.sulfur.dioxide+density+pH+sulphates, data = d_ft)
#perform the predictions
predbic= predict(bic_best, d_ftest)
#Calculate the MSE
msebic = mean((predbic - test_quality)^2)
```

### Stepwise selection through aic and bic

#### AIC
``` {r}
lin = lm(quality~.,data = d_ft)
```
```{r,results='hide'}
AIC_both = step(lin,direction = "both", k=2)
```
for AIC metric total.sulfur.dioxide is the only meaningful predictor defintely in contrast with the previous affirmations
```{r, echo=FALSE,results='hide'}
linaic = lm(quality~total.sulfur.dioxide,data = d_ft)
pred_aic= predict(linaic, d_ftest)
mse_aic = mean((pred_aic - test_quality)^2)
#as expected mse is very high
```
#### BIC
```{r,results='hide'}
rows = nrow(d_ft)
BIC_both = step(lin,direction = "both", k = log(rows))
linbic = lm(quality~chlorides+citric.acid+total.sulfur.dioxide,data = d_ft)
pred_bic= predict(linbic, d_ftest1)
mse_bic = mean((pred_bic - test_quality)^2)
``` 

AIC and BIC (fitted with forward and backward selection) suggest to use just the total.sulfur.dioxide to to implement the model, BIC uses also citric.acid and chlorides 

### Cross validation 

to choose the dimension for the linear model that minimizes the error, we perform best subset selection on the full data set, and select the best variable model. It is important that we make use of the full data set in order to obtain more accurate coefficient estimates

We perform kfold cross validation to choose among all dimension models and find the one that minimizes the error is the one with 10 variables
``` {r}
k <- 10
n <- nrow(data2)
set.seed (1)
folds <- sample( rep (1:k, length = n))
cv.errors <- matrix (NA, k, 11, dimnames = list (NULL , paste (1:11)))
```
there is no predict method for the library so we implemented one
```{r,results='hide'}
predict.regsubsets = function(object, newdata, id, ...) {
  form = as.formula(object$call[[2]])
  mat = model.matrix(form, newdata)
  coefi = coef(object, id = id)
  mat[, names(coefi)] %*% coefi
}
#test= j #train=i
for (j in 1:k) {
  best.fit <- regsubsets(quality~.,data = data2[folds != j, ], nvmax = 11)
  for (i in 1:11) {
    pred <- predict(best.fit , data2[folds == j, ], id = i)
    cv.errors[j, i] <-mean((data2$quality[folds == j] - pred)^2)
  }
}
```
find the MSE
```{r}
mses <- apply(cv.errors , 2, mean)
#plot
par(mfrow = c(1, 1))
plot(mses , type = "b")
min <-which.min(mses)
cross_mse <- mses[min]
```

The best subset selection based on the MSE is a 10-variable model that excludes the variables citric.acid and total.sulfur.dioxide.

### Shrinkage models: RIDGE AND LASSO

First we compute the model matrices to use in both the models and divide in training and test set
``` {r}
dat = as.data.frame(data) #%>%dplyr::select(-quality)
X <- model.matrix(quality~.-1, data = dat)
Y <- dat$quality
Xtr <- model.matrix(quality~.-1, data = d_ft)
Ytr <- d_ft$quality
Xte <- model.matrix(quality~.-1, data = d_ftest1)
Yte <- test_quality
```

#### LASSO

``` {r,results='hide'}
#we fit the model
lasso.fit <- glmnet(Xtr, Ytr, alpha=1)
```
the set of coefficients estimates beta hat for the sequence of lambda provided by glmnet
``` {r,results='hide'}
lasso.fit$beta
lasso.fit$lambda
```

We now plot the lasso regression coefficients as a function of log(lambda) and of the L1 norm
``` {r, echo=FALSE,results='hide',fig.keep='all'}
plot(lasso.fit, label=T)
plot(lasso.fit, label=T, xvar = "lambda")
```

We can see from these plots that depending on the value of the tuning parameter lambda, some of the coefficients will be =0
We now want to pick the best lambda, we're going to do it using k-fold using k=5

``` {r,results='hide',fig.keep='all'}
Lasso.cv <- cv.glmnet(Xtr, Ytr, lambda=seq(0.001, 2, length.out = 100), alpha=1, nfolds=5,
                      family="gaussian")
plot(Lasso.cv) 
```

#### Through Cross validation we find the best lambda and then perform the predictions

``` {r}
bestlam <- Lasso.cv$lambda.min
```

Prediction on the test set and MSE

``` {r,results='hide'}
Lasso.pred <- predict(lasso.fit, s=bestlam, newx=Xte)
mse_Lasso<-mean((Lasso.pred-Yte)^2)
```

And now we show the coefficients for the chosen lambda 
`````` {r}
out <- glmnet(X,Y, alpha=1)
lasso.coef <- predict(out, type="coefficients", s= bestlam)[1:12,]
round(lasso.coef,2)
lasso.coef <-lasso.coef[lasso.coef!=0]
```

### RIDGE

As in lasso we do cross validation to find best lambda
To perform the ridge the procedure is the same but we need to set alpha to 0

``` {r,results='hide'}
ridge.fit <- glmnet(Xtr, Ytr, alpha=0)
ridge.fit$beta
ridge.fit$lambda
```

We now plot the ridge regression coefficients as a function of the L2 norm

```{r, echo=FALSE,results='hide',fig.keep='all'}
l2Betas <- apply(ridge.fit$beta, 2, function(x) sqrt(sum(x^2)))
matplot(l2Betas, t(ridge.fit$beta), type="l")
```

and of log(lambda)

```{r, echo=FALSE,results='hide',fig.keep='all'}
plot(ridge.fit, label=T, xvar = "lambda")
log(ridge.fit$lambda)
``` 

#### k-fold validation to find the best lambda

``` {r}
Ridge.cv <- cv.glmnet(Xtr, Ytr, lambda=seq(0.001, 2, length.out = 100), alpha=0, nfolds=5,
                      family="gaussian")
plot(Ridge.cv) 
```

We then pick the lambda that minimizes the MSE

``` {r}
bestlam <- Ridge.cv$Ridge.min
```

```{r,echo=FALSE,results='hide'}
#Prediction on the test set and MSE
Ridge.pred <- predict(ridge.fit, s=bestlam, newx=Xte)
mse_Ridge<-mean((Ridge.pred-Yte)^2)
```

We can conclude that the shrinkage models that yield the lowest MSE is the Lasso

### Afterward we begin with the nonlinear models:

### Splines

We use manual cross validation to find the degrees of freedom that minimize the MSE and compare Natural Splines, Bsplines and Polynomials
``` {r,results='hide'}
nSpars <- 100
spars <- seq(0.1, 0.99, length.out=nSpars)
```

approximation of cross validation scores

```{r,results='hide',fig.keep='all'}
gcvScores <- matrix(NA, nrow=2, ncol=length(spars))
```

Use 3 degrees

```{r,results='hide',fig.keep='all'}
deg_free <- 3
```

We then plot the MSEs for every knot

```{r,results='hide',fig.keep='all'}
bKnots <- range(data2$alcohol)
# Folds
nfolds <- 10
n <- nrow(data2)
foldid <- sample(1:nfolds, n, replace = T)
# Looping
cvScores <- matrix(NA, nrow=3, ncol=nfolds)
rownames(cvScores) <- c("Polynomial", "Natural Splines", "B-Spline")
for (i in 1:nfolds)
{
  datIn <- data2 %>% filter(foldid!=i)
  datOut <- data2 %>% filter(foldid==i)
  
  oo1 <- lm(quality~poly(alcohol, degree = deg_free), data=datIn)
  pred1 <- predict(oo1, datOut)
  cvScores[1, i] <- mean((pred1-datOut$quality)^2)
  oo2 <- lm(quality~ns(x=alcohol, df = deg_free, Boundary.knots = bKnots), data=datIn)
  pred2 <- predict(oo2, datOut)
  cvScores[2, i] <- mean((pred2-datOut$quality)^2)
  oo3 <- lm(quality~bs(x=alcohol, df = deg_free, Boundary.knots = bKnots), data=datIn)
  pred3 <- predict(oo3, datOut)
  cvScores[3, i] <- mean((pred3-datOut$quality)^2)
}
```

Errors on each fold for every model

```{r,fig.keep='all'}
t(cvScores) %>% as_tibble() %>% mutate(id=1:nrow(.)) %>% gather(Model, MSE, -id) %>%  
  ggplot() + geom_point(aes(x=id, y=MSE, col=Model, shape=Model), size=2, alpha=0.7) + theme_bw()
# Average error for every method used, we see that Natural Splines have least error 
rowMeans(cvScores)
```

Now we evaluate the mean square error of each model for different degrees of freedom

```{r, echo=FALSE,results='hide',fig.keep='all'}
# Double looping
# dfs
dfree <- 3:12
# Double looping
cvScores1 <- matrix(NA, nrow=3, ncol=length(dfree))
rownames(cvScores1) <- c("Polynomial", "Natural Splines", "B-Spline")
colnames(cvScores1) <- dfree
for (j in 1:length(dfree))
{
  # Looping
  cvScores2 <- matrix(NA, nrow=3, ncol=nfolds)
  for (i in 1:nfolds)
  {
    datIn <- data2 %>% filter(foldid!=i)
    datOut <- data2 %>% filter(foldid==i)
    
    oo1 <- lm(quality~poly(alcohol, degree = dfree[j]), data=datIn)
    pred1 <- predict(oo1, datOut)
    cvScores2[1, i] <- mean((pred1-datOut$quality)^2)
    oo2 <- lm(quality~ns(x=alcohol, df = dfree[j], Boundary.knots = bKnots), data=datIn)
    pred2 <- predict(oo2, datOut)
    cvScores2[2, i] <- mean((pred2-datOut$quality)^2)
    oo3 <- lm(quality~bs(x=alcohol, df = dfree[j], Boundary.knots = bKnots), data=datIn)
    pred3 <- predict(oo3, datOut)
    cvScores2[3, i] <- mean((pred3-datOut$quality)^2)
  }
  
  # Saving for current df
  cvScores1[, j] <- rowMeans(cvScores2)
}

t(cvScores1) %>% as_tibble() %>% mutate(df=dfree) %>% gather(key, MSE, -df) %>%  
  ggplot() + geom_line(aes(x=df, y=MSE, col=key)) + theme_bw()
```

The best choice of degrees of freedom seems to be somewhere between 5 and 10
we can go a bit further with degree of freedom for natural splines
with too much complexity polynomial is the one performing worse cause it has non additional constraints

We pick for natural is at 11 dfs and for b-splines is 10. For polynomials around 7

So then we fit the models and perform the predictions

```{r, echo=FALSE,results='hide',fig.keep='all'}
#First we fit the B-splines
b_splines <- lm(quality~bs(alcohol, df = 10), data = d_ft)
predbsplines= predict(b_splines, d_ftest)
#Calculate the MSE
msebsplines = mean((predbsplines- test_quality)^2)

#We then fit natural splines
n_splines <-lm(quality~ns(alcohol, df = 11), data = d_ft)
prednsplines= predict(n_splines, d_ftest)
#Calculate the MSE
msensplines = mean((prednsplines- test_quality)^2)

#lastly the polynomial
polynomial <- lm(quality~poly(alcohol, df = 7), data = d_ft)
polynomial= predict(polynomial, d_ftest)
#Calculate the MSE
msepolynomials = mean((polynomial- test_quality)^2)
data2<-data.frame(data)
```

Last model for predictions is the 

### Decision trees

``` {r, echo=FALSE,results='hide',fig.keep='all'}
library(tree)
require(tree)
```
```{r, results='hide',fig.keep='all'}
#Regression tree fit
fit_tr = tree(quality~., data=d_ft)
summary(fit_tr)
plot(fit_tr, col="grey")
text(fit_tr, pretty=0, cex = 0.7)
#make the predictions
pred_test = predict(fit_tr, d_ftest)
```
```{r, echo=FALSE,results='hide',fig.keep='all'}
#Calculate the MSE
msedecisiontree<-mean((pred_test - test_quality)^2)
msedecisiontree
var(test_quality)
```

We want to see if tree pruning improves the performance of the tree: to do so we run a K-fold cross-validation and we evaluate the mean squared prediction error on the data in the left-out kth fold, as a function of k.

``` {r, echo=FALSE,results='hide'}
fit_cvtr = cv.tree(fit_tr)
par(mfrow = c(1,2))
#We now plot the error against the cost-complexity parameter k and the size of the tree
plot(fit_cvtr$size, fit_cvtr$dev/nrow(d_ftest), type = "b",col="blue", xlab="Size", ylab="Err")
plot(fit_cvtr$k, fit_cvtr$dev/nrow(d_ftest), type="b", col=3, xlab="k", ylab="Err")
```

From the plot we can see that the pruning would not benefit to the performance of the model, but we perform the tree pruning anyways (to confirm our assumption) with tree size=5 and pruning parameter=50

#### Pruning

``` {r,results='hide',fig.keep='all'}
fit_pr = prune.tree(fit_tr, best = 5, k=50)
par(mfrow=c(1,1))
plot(fit_pr, col="grey")
text(fit_pr, pretty=0, cex = 0.7)
``` 

We use our pruned tree to make predictions on the test set and compute the MSE

``` {r, echo=FALSE,results='hide'}
par(mfrow=c(1,1))
pred_pr = predict(fit_pr, d_ftest)
msepruning<-mean((pred_pr - test_quality)^2)
plot(pred_pr, test_quality, col="darkblue", xlab="predicted", ylab="test")
abline(0,1, col=2)
```

Then we do the Random Forests: starting from all the predictors (bagging)

``` {r, echo=FALSE,results='hide'}
library(randomForest)
```

#### Bagging 

We perform bagging by exploiting the randomForest function and considering all of our predictors for each split of the tree

```{r}
fit_bag = randomForest(quality~., data = d_ft, mtry = ncol(d_ft)-1, importance = T)
```
```{r, echo=FALSE,results='hide'}
#make the predictions
pred_bag = predict(fit_bag, d_ftest)
msebagging<-mean((pred_bag - test_quality)^2)
plot(pred_bag, test_quality, col="darkblue", xlab="predicted", ylab="test")
abline(0,1, col=2)
```

The test set MSE associated with the bagged regression tree is lower than the one obtained with the regression tree.

### Random forest

Then we fit a random forest with just 2 predictors

``` {r}
fit_rf = randomForest(quality~., data = d_ft, mtry = 2, importance = T, ntree=1e3 )
```

After we make the predictions and evaluate the MSE.

```{r, echo=FALSE,results='hide'}
pred_rf = predict(fit_rf, d_ftest)
mse_randomf<-mean((pred_rf - test_quality)^2)
plot(pred_rf, test_quality, col="darkblue", xlab="predicted", ylab="test")
abline(0,1, col=2)
``` 

the MSE of the random forest yields an improvement over the bagging 
Plot the importance of each variable

```  {r}
importance(fit_rf)
varImpPlot(fit_rf)
``` 

The alcohol is the most important variables followed by the free.sulfur.dioxide and volatile acidity.

## Point 6 
### Compare the results

```  {r}
vector<-c(msebic,mse_aic,mse_bic,cross_mse,mse_Ridge,mse_Lasso,msebsplines,msensplines,msepolynomials,msedecisiontree,msepruning, msebagging, mse_randomf)
vector
min(vector)
``` 
the model with the least MSE is the model fitted with the cross validation selection knit

## Conclusion:
By evaluating the MSE on the test set for every model, we observed that the best model is the cross-validation model. It selects a linear multiple regression with 10 predictors (every variable except for total.sulfur.dioxide) with a MSE of approximately 0,51.
So we can conclude that our data can be interpreted through a linear model.
